Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-28 paper_comparison/appendix.Rmd
update lv plot legend

vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  ungroup() %>%
  filter(type == "non-linearity") %>%
  select(type, exp, prop_detect) %>%
  mutate(exp = as.character(exp)) %>%
  sample_from_null(7) %>%
  ggplot() +
  geom_lv(aes(x = exp, y = prop_detect, fill = after_stat(LV)), varwidth = TRUE, k = 4) +
  scale_alpha_discrete(range = c(0.7, 0)) +
  # scale_fill_lv() +
  facet_wrap(~k, ncol = 5) +
  theme_light() +
  scale_x_discrete(labels = c("I", "III")) +
  labs(fill = "Quantiles") +
  scale_fill_discrete(labels = c("50%", "25% - 75%", "12.5% - 87.5%", "6.25% - 93.75%")) +
  ylab("Weighted propotion of detect") +
  xlab("Data collection period")
```

```{r heter-boxplot-lineup, fig.cap = '\\label{fig:heter-boxplot-lineup}A lineup of "letter-value" boxplots of weighted propotion of detect for lineups over different data collection periods for heteroskedasticity model. Can you find the most different boxplot? The data plot is positioned in panel $2^4 - 2$.'}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  ungroup() %>%
  filter(type != "non-linearity") %>%
  select(type, exp, prop_detect) %>%
  mutate(exp = as.character(exp)) %>%
  sample_from_null(14) %>%
  ggplot() +
  geom_lv(aes(x = exp, y = prop_detect, fill = after_stat(LV)), varwidth = TRUE, k = 4) +
  facet_wrap(~k, ncol = 5) +
  theme_light() +
  scale_x_discrete(labels = c("II", "III")) +
  labs(fill = "Quantiles") +
  scale_fill_discrete(labels = c("50%", "25% - 75%", "12.5% - 87.5%", "6.25% - 93.75%")) +
  ylab("Weighted propotion of detect") +
  xlab("Data collection period")
```

>>>>

vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  ungroup() %>%
  filter(type == "non-linearity") %>%
  select(type, exp, prop_detect) %>%
  mutate(exp = as.character(exp)) %>%
  sample_from_null(7) %>%
  ggplot() +
  geom_lv(aes(x = exp, y = prop_detect, fill = after_stat(LV)), varwidth = TRUE, k = 4) +
  scale_alpha_discrete(range = c(0.7, 0)) +
  facet_wrap(~k, ncol = 5) +
  theme_light() +
  scale_x_discrete(labels = c("I", "III")) +
  labs(fill = "Quantiles") +
  scale_fill_manual(labels = c("0.5", "[0.25, 0.75]", "[0.125, 0.875]", "[0.0625, 0.09375]"),
                    values = c("white", rev(RColorBrewer::brewer.pal(5, "Blues")))) +
  ylab("Weighted propotion of detect") +
  xlab("Data collection period")
```

```{r heter-boxplot-lineup, fig.cap = '\\label{fig:heter-boxplot-lineup}A lineup of "letter-value" boxplots of weighted propotion of detect for lineups over different data collection periods for heteroskedasticity model. Can you find the most different boxplot? The data plot is positioned in panel $2^4 - 2$.'}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  ungroup() %>%
  filter(type != "non-linearity") %>%
  select(type, exp, prop_detect) %>%
  mutate(exp = as.character(exp)) %>%
  sample_from_null(14) %>%
  ggplot() +
  geom_lv(aes(x = exp, y = prop_detect, fill = after_stat(LV)), varwidth = TRUE, k = 4) +
  facet_wrap(~k, ncol = 5) +
  theme_light() +
  scale_x_discrete(labels = c("II", "III")) +
  labs(fill = "Quantiles") +
  scale_fill_manual(labels = c("0.5", "[0.25, 0.75]", "[0.125, 0.875]", "[0.0625, 0.09375]"),
                    values = c("white", rev(RColorBrewer::brewer.pal(5, "Blues")))) +
  ylab("Weighted propotion of detect") +
  xlab("Data collection period")
```
